### 2019-05-07 paper/plots/mc/plot.tex
added tikz plots

\pgfplotstableread[col sep = comma]{./OPTIMIST.csv}\optimist
\pgfplotstableread[col sep = comma]{./GPUCB.csv}\gpucb
\pgfplotstableread[col sep = comma]{./UCB1.csv}\ucb

@@

\newcommand\drawplot[5]{
	\addplot table[x=iteration, y={#2}]{#5};\label{plots:#1}
	\def\temp{#3}\ifx\temp\empty
	\else
		\addplot[name path=up, draw=none, forget plot] table[x=iteration, y={#3}]{#5};
    	\addplot[name path=low, draw=none, forget plot] table[x=iteration, y={#4}]{#5};
    	\addplot[/pgfplots/refstyle={plots:#1}, fill opacity=0.2, forget plot] fill between[of=up and low];
	\fi
	\addlegendentry{#1}
}

@@

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={10}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=6cm,
                      		  width=7cm,  
                      		  ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.48,0.95)},anchor=north east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Regret}]

        			\drawplot{OPTIMIST}{mean}{up}{low}{\optimist}
        			\drawplot{UCB1}{mean}{up}{low}{\ucb}
        			\drawplot{GPUCB}{mean}{up}{low}{\gpucb}

>>>>

\pgfplotstableread[col sep = comma]{./OPTIMIST.csv}\optimist
\pgfplotstableread[col sep = comma]{./PGPE.csv}\pgpe
\pgfplotstableread[col sep = comma]{./PBPOIS.csv}\pbpois

@@

\newcommand\drawplot[6]{
	\def\todraw{#1}\ifx\todraw\empty
		\addplot[draw=none] coordinates {(1,1)};
	\else
		\addplot table[x=iteration, y={#2}, each nth point={#6}]{#5};\label{plots:#1}
		%\addlegendentry{#1}
		\def\temp{#3}\ifx\temp\empty
		\else
			\addplot[name path=up, draw=none, forget plot] table[x=iteration, y={#3}]{#5};
    		\addplot[name path=low, draw=none, forget plot] table[x=iteration, y={#4}]{#5};
    		\addplot[/pgfplots/refstyle={plots:#1}, fill opacity=0.2, forget plot] fill between[of=up and low];
		\fi
	\fi
}

@@

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=6cm,
                      		  width=7cm,  
                      		  ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.95,0.05)},anchor=south east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Average Return}]

        			\drawplot{OPTIMIST}{mean}{up}{low}{\optimist}{4}
        			\drawplot{}{}{}{}{}{}
        			\drawplot{}{}{}{}{}{}
        			\drawplot{PGPE}{mean}{up}{low}{\pgpe}{1}
        			\drawplot{PB-POIS}{mean}{up}{low}{\pbpois}{1}
        			\legend{OPTIMIST,,,PGPE, PB-POIS};
